Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2021-01-14 vesicle_code/docs/permeableVes/main.tex
touched up supp material

The governing equations are non-dimensionalized by using a 
characteristic length scale $R_0 = 10^{-6}$m, a bending stiffness of
$k_b = 10^{-19}$J and fluid viscosity $5 \times 10^{-2}$kg/ms. We scale time by $\tau\equiv\mu R_0^3/k_b = 0.5s$, 
the velocity by $R_0/\tau = 2\mu$m/s, the pressure by $k_b/R_0^3 = 10^{-1}$Pa, 
tension by $k_b/R_0^2 = 10^{-7}$N/m, and the permeability by $R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. 
Under this nondimensionalization, a two-dimensional semipermeable vesicle in a viscous fluid is characterized by 
(a) its reduced area $\alpha = 4\pi A/L^2
\in (0,1]$, where $L$ is the vesicle length and $A$ is its area, and 
(b) its permeability $\beta = k_w/(R_0\mu)$.
In two dimensions, the membrane length is conserved by the local inextensibility condition, 
but the enclosed area is not because of semipermeability. Therefore, the reduced area is
dynamic.

Since the fluid satisfies the Stokes equations, the velocity and
pressure can be represented as layer potentials. Given the interfacial
boundary conditions~\eqref{eqn:jump}, the fluid velocity is
\begin{align}
  \uu(\xx) = \uu_\infty(\xx) + \SS[\ff_\mathrm{mem}](\xx), \quad
    \xx \in \Omega,
\end{align}
where $\SS$ is the single-layer potential
\begin{align}
  \SS[\ff](\xx) = \frac{1}{4\pi} \int_{\gamma} \left(
    -\mathbf{I} \log\rho + \frac{\rr \otimes \rr}{\rho^2} \right)
    \ff(\yy) ds_{\yy},
%  \SS[\ff](\xx) = \frac{1}{4\pi\mu} \int_{\gamma} \left(
%    -\mathbf{I} \log\rho + \frac{\rr \otimes \rr}{\rho^2} \right)
%    \ff(\yy) ds_{\yy},
\end{align}
with $\rr = \xx - \yy$ and $\rho = |\rr|$. Imposing the flux
condition~\eqref{eqn:vesicleFlux} and the inextensibility condition, the
vesicle velocity satisfies the boundary integral equation
\begin{align}
  \label{eqn:vesVelocity}
  \dot{\xx} &= \uu_\infty(\xx) + \beta (\ff_\mathrm{mem}\cdot\nn)\nn
  + \SS [\ff_\mathrm{mem}](\xx),  \quad
  \xx_s \cdot \dot{\xx}_s = 0.
\end{align}
%where $\beta = k_w/W$ is the dimensionless water permeability. 
In confined geometries, the far field term $\uu_\infty$ is replaced by a
double-layer potential with a density defined on $\partial\Omega$. The
unknown density function allows us to satisfy the Dirichlet boundary
condition $\uu(\xx) = \UU(\xx)$ for $\xx \in \partial\Omega$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Numerical Validation}
To validate our methods, we construct a phase diagram of the steady
state shape of an impermeable vesicle in a Poiseuille flow. Depending on
the flow rate and the reduced area, the steady state vesicle becomes
either a axisymmetric bullet, a axisymmetric parachute, or a tank
treading asymmetric slipper~\cite{kao-bir-mis2009}. Comparing our
results (Figure~\ref{fig:PoiseuillePhase}) with those
in~\cite{kao-bir-mis2009} (see Figure 2), we see that the vesicle shapes
qualitatively agree. We note that Kaoui {\em et al.}~report that the
vesicles with $\alpha=0.7$ and flow rates $U = 1200 \mu$ m/s and $U =
1600 \mu$m/s are axisymmetric.  In our simulations these vesicles are
slightly asymmetric, are undergoing a tank treading motion, and we
therefore report them as asymmetric slippers.
\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/parabolicImpermeable.tikz}
  \else
  \includegraphics{figures/parabolicImpermeable.pdf}
  \fi
  \caption{\label{fig:PoiseuillePhase} Phase diagram of an impermeable
  vesicle with various reduced areas submerged in a Poiseuille flow with
  various flow rates. The shapes agree qualitatively with Kaoui {\em et
  al.}~\cite{kao-bir-mis2009} (see Figure 2).}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Supplementary Material: Vesicle Area}
In the absence of an imposed flow, the steady state vesicle shape and a
differential equation for the area of the vesicle can be derived. We
start by following the analysis of Veerapaneni {\em et
al.}~\cite{vee-raj-bir-pur2009} by computing the steady state shape of a
semipermeable vesicle in a quiescent flow. The steady state shape is a
stationary point of the Lagrangian
\begin{align}
  \mathcal{L} = \frac{1}{2}\int_{\gamma} \kappa^2 \, ds +
    \Lambda \left(\int_{\gamma} ds  - L \right),
\end{align}
where the Lagrange multiplier $\Lambda$ is the tension. Note the absence
of the pressure Lagrange multiplier since the vesicle's area fluctuates.
Taking the variation of $\mathcal{L}$ with respect to $\gamma$ and
setting it to zero, the steady state shape satisfies $\kappa_{ss} +
\frac{1}{2}\kappa^3 - \Lambda \kappa = 0$, with initial conditions
$\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.  Integrating once, we have
\begin{align}
  \frac{\kappa_s^2}{2} + \frac{\kappa^4}{8} - 
    \frac{\Lambda}{2}\kappa^2 = \frac{\kappa_0^4}{8} - 
    \frac{\Lambda}{2}\kappa_0^2.
  \label{eqn:curveODE}
\end{align}
Assuming $\kappa_s \neq 0$,~\eqref{eqn:curveODE} is separable, and can
be solved analytically in terms of the {\em EllipticF} function using
Mathematica. Unlike in the impermeable case, the solution
of~\eqref{eqn:curveODE} is not periodic unless $\kappa(s) = \kappa_0$.
Therefore, the steady state shape of a semipermeable vesicle in a
quiescent flow is a circle with radius $L/2\pi$ and constant tension
$\Lambda = \kappa^2/2 = 2\pi^2/L^2.$ Note that in contrast to a
impermeable vesicle, the tension is positive rather than negative.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Supplementary Material: Vesicle Tensions}

\subsection*{Vesicle Relaxation}
Figure~\ref{fig:relaxationTensions} shows the membrane tension
distribution along the relaxing vesicles in
Figure~\ref{fig:relaxationComposite}. The membrane tension (color bars)
is in N/m. As the semipermeable vesicle relaxes, the membrane tension
reduces in magnitude and becomes more evenly distributed along the
membrane. In the top row the vesicle nearly relaxes to a circle on the
right, and the membrane tension is uniform and equal to $k_b \kappa^2/2$
as predicted by our analysis (see Eq.~\ref{eqn:areaROC}). In the bottom
row, the initial vesicle shape has a lot of high curvature regions (and
thus the low reduced area), and it takes more than four hours to inflate
to twice the total water content for $\beta=10^{-7}$. In contrast the
water enclosed inside the vesicle in the top row remains nearly constant
in four hours.
\begin{figure*}[htp]
  \includegraphics[width=\textwidth]{figures/relaxationTensions2.pdf}

%  \centering
%  \ifTikz
%    \input{figures/relaxationTensions.tikz}
%  \else
%    \includegraphics{figures/relaxationTensions.pdf}
%  \fi
  \caption{\label{fig:relaxationTensions} Tension distribution of vesicles in
  relaxation that corresponds to Figure~\ref{fig:relaxationComposite}.}
\end{figure*}

\subsection*{Vesicle in a planar shear flow}
Our integral simulations of a semipermeable vesicle in a planar shear flow show that the equilibrium
vesicle shape depends mostly on the capillary number $Ca_\mathrm{E}$, independent of the dimensionless water permeability $\beta$.
Our simulations show that the time it takes for a semipermeable vesicle to reach equilibrium in a planar shear flow is inversely proportional to $\beta$, just like the relaxing vesicle.
The tension distribution along the equilibrium vesicle at $\beta=10^{-4}$ is shown in Figure~\ref{fig:shearTensions}, where the color bars are for the membrane tension in N/m.
The capillary number $Ca_\mathrm{E}$ increases from Figure~\ref{fig:shearTensions}(a) to (g), and we observe that the tension magnitude also increases almost linearly with
$Ca_\mathrm{E}$.  We also observe that the membrane tension is relatively small at the tip when the membrane curvature is large due to the extensional component in the shear flow.
\begin{figure*}[hbp]
  \begin{tikzpicture}[scale=1]
    \node[inner sep=0pt] at (0,0) {
    \includegraphics[width=\textwidth]{figures/shearTensions.pdf}
    };
    \node at (-8.54,0.6) {(a)};
    \node at (-6.00,0.6) {(b)};
    \node at (-3.46,0.6) {(c)};
    \node at (-0.92,0.6) {(d)};
    \node at (+1.60,0.6) {(e)};
    \node at (+4.16,0.6) {(f)};
    \node at (+6.70,0.6) {(g)};
  \end{tikzpicture}
%  \includegraphics[width=\textwidth]{figures/shearTensions.pdf}
  \caption{\label{fig:shearTensions} Tension distribution along a vesicle in
  a linear shear flow. The semi-permeability constant is $\beta = 10^{-4}$ for
  all these cases, and the elastic capillary number ranges from
  $10^{-1}$ to $10^{2}$ as in Figure~\ref{fig:shearComposite}.}
\end{figure*}

\subsection*{Vesicle in a Poiseuille flow}
In a nonlinear shear flow, an impermeable vesicle can reach equilibrium position at the mid-plane of the shear flow
for sufficiently large reduced area, regardless of the maximum flow velocity $U$. For a semi-permeable vesicle, however,
our simulation results (summarized in Figure~\ref{fig:parabolicComposite}) show that the equilibrium vesicle shape (and position) is determined by $U$, 
and independent of the initial vesicle reduced area and permeability $\beta$. The corresponding membrane tension distribution is shown in Figure~\ref{fig:parabolicTensions} as a function of flow velocity $U$ from $200\mu$m/s  to $800\mu$m/s.
\begin{figure*}[hbp]
  \centering
  \begin{tikzpicture}[scale=1]
    \node[inner sep=0pt] at (0,0) {
    \includegraphics[width=\textwidth]{figures/parabolicTensions.pdf}
    };
    \node at (-8.2,1.5) {(a)};
    \node at (-3.8,1.5) {(b)};
    \node at (+0.6,1.5) {(c)};
    \node at (+5.0,1.5) {(d)};
  \end{tikzpicture}
  \caption{\label{fig:parabolicTensions} The equilibrium tension
  distribution of a semipermeable vesicle with $\beta=10^{-3}$ in a parabolic
  flow (see Figure~\ref{fig:parabolicComposite}). The flow velocities
  are (a) 200$\mu$m/s, (b) 400$\mu$m/s, (c) 600$\mu$m/s, and (d)
  800$\mu$m/s.}
\end{figure*}

@@

\subsection*{Vesicle in a closely-fit channel}
When a semi-permeable vesicle goes through a closely-fit channel, we observe that the water efflux is found in the front, and the influx is in the rear of the vesicle membrane (Figure~\ref{fig:stenosisComposite}). This corresponds well to the corresponding tension distribution in Figure~\ref{fig:stenosisTensions}: Larger tension in the front, and smaller tension in the rear.
\begin{figure*}[htp]
  \centering
  \begin{tikzpicture}[scale=1]
    \node[inner sep=0pt] at (0,0) {
    \includegraphics[width=\textwidth]{figures/stenosisTensions.pdf}
    };
    \node at (-8.6,0.7) {(a)};
    \node at (-1.6,0.7) {(b)};
  \end{tikzpicture}
  \caption{\label{fig:stenosisTensions} Tension distribution along a semi-permeable vesicle going through a closely-fit channel.}
\end{figure*}

\subsection*{Vesicle going through a contracting channel (slit)}
When a semipermeable vesicle goes through a contracting channel (slit)
the numerical simulations show that both the driving flow and the
membrane permeability have to be sufficiently large for a successful
passage through the slit, see Figure~\ref{fig:contractingComposite}.  As
the vesicle goes through the contracting channel, the gradual
confinement first leads to a slow inflation. Once the vesicle is close
to the neck, it quickly deflates in order to fit the constriction. When
the vesicle is near the neck, simulations show that the water efflux is
in the front and rear of vesicle while most water influx is in the
middle. The tension distribution along the vesicle as a function of
their position in the contracting channel is summarized in
Figure~\ref{fig:contractingTensions1}, where we observe the membrane
tension has the largest magnitude when the vesicle is at the neck. Away
from the neck the membrane tension is quite small due to th
\begin{figure*}[htp]
  \centering
  \begin{tikzpicture}[scale=1]
    \node[inner sep=0pt] at (0,0) {
    \includegraphics[width=\textwidth]{figures/contractingTensions1.pdf}
    };
    \node at (-8.62,4.3) {(a)};
    \node at (+1.1,4.3) {(c)};
    \node at (-8.62,-1.2) {(b)};
    \node at (+1.1,-1.2) {(d)};
  \end{tikzpicture}
  \begin{tikzpicture}[scale=1]
    \node[inner sep=0pt] at (0,0) {
    \includegraphics[width=0.8\textwidth]{figures/contractingTensions2.pdf}
    };
    \node at (-6.79,1.4) {(e)};
  \end{tikzpicture}
  \caption{\label{fig:contractingTensions1} Tension distribution along a
  semi-permeable vesicle going through a contracting geometry. The
  vesicle tension increases by up to five orders of magnitude when as it
  enters the neck. The permeability constant and flow rates are (a)
  $U_{\max} = 5.7\mu$m/s, $\beta = 5 \times 10^{-4}$; (b) $U_{\max} =
  5.7\mu$m/s, $\beta = 5 \times 10^{-3}$; (c) $U_{\max} = 0.57\mu$m/s,
  $\beta = 1 \times 10^{-3}$; (d) $U_{\max} = 5.7\mu$m/s, $\beta = 1
  \times 10^{-3}$; (e) $U_{\max} = 18\mu$m/s, $\beta = 1 \times
  10^{-3}$.}
\end{figure*}

>>>>

The governing equations are non-dimensionalized by using a
characteristic length scale $R_0 = 10^{-6}$m, a bending stiffness of
$k_b = 10^{-19}$J, and fluid viscosity $5 \times 10^{-2}$kg/ms. We scale
time by $\tau\equiv\mu R_0^3/k_b = 0.5s$, the velocity by $R_0/\tau =
2\mu$m/s, the pressure by $k_b/R_0^3 = 10^{-1}$Pa, tension by $k_b/R_0^2
= 10^{-7}$N/m, and the permeability by $R_0\mu = 2 \times
10^{-5}$m$^2$s/kg. Under this nondimensionalization, a two-dimensional
semipermeable vesicle in a viscous fluid is characterized by (a) its
reduced area $\alpha = 4\pi A/L^2 \in (0,1]$, where $L$ is the vesicle
length and $A$ is its area, and (b) its permeability $\beta =
k_w/(R_0\mu)$. In two dimensions, the membrane length is conserved by
the local inextensibility condition, but the enclosed area is not
because of semipermeability. Therefore, the reduced area is dynamic.

Since the fluid satisfies the Stokes equations, the velocity and
pressure can be represented as layer potentials. Given the interfacial
boundary conditions~\eqref{eqn:jump}, the fluid velocity is
\begin{align}
  \uu(\xx) = \uu_\infty(\xx) + \SS[\ff_\mathrm{mem}](\xx), \quad
    \xx \in \Omega,
\end{align}
where $\SS$ is the single-layer potential
\begin{align}
  \SS[\ff](\xx) = \frac{1}{4\pi} \int_{\gamma} \left(
    -\mathbf{I} \log\rho + \frac{\rr \otimes \rr}{\rho^2} \right)
    \ff(\yy) ds_{\yy},
%  \SS[\ff](\xx) = \frac{1}{4\pi\mu} \int_{\gamma} \left(
%    -\mathbf{I} \log\rho + \frac{\rr \otimes \rr}{\rho^2} \right)
%    \ff(\yy) ds_{\yy},
\end{align}
with $\rr = \xx - \yy$ and $\rho = |\rr|$. Imposing the flux
condition~\eqref{eqn:vesicleFlux} and the inextensibility condition, the
vesicle velocity satisfies the boundary integral equation
\begin{align}
  \label{eqn:vesVelocity}
  \dot{\xx} &= \uu_\infty(\xx) + \beta (\ff_\mathrm{mem}\cdot\nn)\nn
  + \SS [\ff_\mathrm{mem}](\xx),  \quad
  \xx_s \cdot \dot{\xx}_s = 0.
\end{align}
In confined geometries, the far field term $\uu_\infty(\xx)$ is replaced
by a double-layer potential with a density defined on $\partial\Omega$.
The unknown density function allows us to satisfy the Dirichlet boundary
condition $\uu(\xx) = \UU(\xx)$ for $\xx \in \partial\Omega$.

@@

\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/parabolicImpermeable.tikz}
  \else
  \includegraphics{figures/parabolicImpermeable.pdf}
  \fi
  \caption{\label{fig:PoiseuillePhase} Phase diagram of an impermeable
  vesicle with various reduced areas submerged in a Poiseuille flow with
  various flow rates. The shapes agree qualitatively with Kaoui {\em et
  al.}~\cite{kao-bir-mis2009} (see Figure 2).}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Numerical Validation}
To validate our methods, we construct a phase diagram of the steady
state shape of an impermeable vesicle in a Poiseuille flow. Depending on
the flow rate and the reduced area, the steady state vesicle is either a
axisymmetric bullet, a axisymmetric parachute, or a tank treading
asymmetric slipper~\cite{kao-bir-mis2009}. Comparing our results
(Figure~\ref{fig:PoiseuillePhase}) with those in~\cite{kao-bir-mis2009}
(see Figure 2), we see that the vesicle shapes qualitatively agree. We
note that Kaoui {\em et al.}~report that the vesicles with $\alpha=0.7$
and flow rates $U = 1200 \mu$m/s and $U = 1600 \mu$m/s are axisymmetric.
In our simulations these vesicles are slightly asymmetric, are
undergoing a tank treading motion, and we therefore report them as
asymmetric slippers.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Supplementary Material: Vesicle Area}
In the absence of an imposed flow, the steady state vesicle shape and a
differential equation for the area of the vesicle can be derived. We
start by following the analysis of Veerapaneni {\em et
al.}~\cite{vee-raj-bir-pur2009} by computing the steady state shape of a
semipermeable vesicle in a quiescent flow. The steady state shape is a
stationary point of the Lagrangian
\begin{align}
  \mathcal{L} = \frac{1}{2}\int_{\gamma} \kappa^2 \, ds +
    \Lambda \left(\int_{\gamma} ds  - L \right),
\end{align}
where the Lagrange multiplier $\Lambda$ is the tension. Note the absence
of the pressure Lagrange multiplier since the vesicle's area fluctuates.
Taking the variation of $\mathcal{L}$ with respect to $\gamma$ and
setting it to zero, the steady state shape satisfies $\kappa_{ss} +
\frac{1}{2}\kappa^3 - \Lambda \kappa = 0$, with initial conditions
$\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.  Integrating once, we have
\begin{align}
  \frac{\kappa_s^2}{2} + \frac{\kappa^4}{8} - 
    \frac{\Lambda}{2}\kappa^2 = \frac{\kappa_0^4}{8} - 
    \frac{\Lambda}{2}\kappa_0^2.
  \label{eqn:curveODE}
\end{align}
Assuming $\kappa_s \neq 0$,~\eqref{eqn:curveODE} is separable, and can
be solved analytically in terms of the {\em EllipticF} function using
Mathematica. Unlike in the impermeable case, the solution
of~\eqref{eqn:curveODE} is not periodic unless $\kappa(s) = \kappa_0$.
Therefore, the steady state shape of a semipermeable vesicle in a
quiescent flow is a circle with radius $L/2\pi$ and constant tension
$\Lambda = \kappa^2/2 = 2\pi^2/L^2.$ Note that in contrast to a
impermeable vesicle, the steady state tension is positive rather than
negative.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Supplementary Material: Vesicle Tensions}
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{figures/relaxationTensions2.pdf}
%  \ifTikz
%    \input{figures/relaxationTensions.tikz}
%  \else
%    \includegraphics{figures/relaxationTensions.pdf}
%  \fi
  \caption{\label{fig:relaxationTensions} The tension distribution of
  vesicles in relaxation that corresponds to
  Figure~\ref{fig:relaxationComposite}.}
\end{figure*}

\subsection*{Vesicle Relaxation}
Figure~\ref{fig:relaxationTensions} shows the membrane tension
distribution along the relaxing vesicles in
Figure~\ref{fig:relaxationComposite}. The membrane tension (color bars)
is in N/m. As the semipermeable vesicle relaxes, the membrane tension
reduces in magnitude and becomes more evenly distributed along the
membrane. In the top row the vesicle nearly relaxes to a circle on the
right, and the membrane tension is uniform and equal to $k_b \kappa^2/2$
as predicted by our analysis (see \eqref{eqn:areaROC}). In the bottom
row, the initial vesicle shape has a lot of high curvature regions (and
thus the low reduced area), and it takes more than four hours to inflate
to twice the total water content for $\beta=10^{-7}$. In contrast the
water enclosed inside the vesicle in the top row remains nearly constant
in four hours.
\todo[inline]{I don't understand this last sentence}

\subsection*{Vesicle in a planar shear flow}
Our simulations of a semipermeable vesicle in a planar shear flow show
that the equilibrium vesicle shape depends mostly on the capillary
number $Ca_\mathrm{E}$, independent of the dimensionless water
permeability $\beta$. Our simulations show that the time it takes for a
semipermeable vesicle to reach equilibrium in a planar shear flow is
inversely proportional to $\beta$, just like the relaxing vesicle. The
tension distribution along the equilibrium vesicle at $\beta=10^{-4}$ is
shown in Figure~\ref{fig:shearTensions}, where the color bars are for
the membrane tension in N/m. The capillary number $Ca_\mathrm{E}$
increases from Figure~\ref{fig:shearTensions}(a) to (g), and we observe
that the tension magnitude also increases almost linearly with
$Ca_\mathrm{E}$. We also observe that the membrane tension is relatively
small at the tip when the membrane curvature is large due to the
extensional component in the shear flow.
\begin{figure*}[hbp]
  \begin{tikzpicture}[scale=1]
    \node[inner sep=0pt] at (0,0) {
    \includegraphics[width=\textwidth]{figures/shearTensions.pdf}
    };
    \node at (-8.54,0.6) {(a)};
    \node at (-6.00,0.6) {(b)};
    \node at (-3.46,0.6) {(c)};
    \node at (-0.92,0.6) {(d)};
    \node at (+1.60,0.6) {(e)};
    \node at (+4.16,0.6) {(f)};
    \node at (+6.70,0.6) {(g)};
  \end{tikzpicture}
%  \includegraphics[width=\textwidth]{figures/shearTensions.pdf}
  \caption{\label{fig:shearTensions} The tension distribution along a
  vesicle in a linear shear flow. The semi-permeability constant is
  $\beta = 10^{-4}$ for all these cases, and the elastic capillary
  number ranges from $10^{-1}$ to $10^{2}$ as in
  Figure~\ref{fig:shearComposite}.}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \begin{tikzpicture}[scale=1]
    \node[inner sep=0pt] at (0,0) {
    \includegraphics[width=\textwidth]{figures/parabolicTensions.pdf}
    };
    \node at (-8.2,1.5) {(a)};
    \node at (-3.8,1.5) {(b)};
    \node at (+0.6,1.5) {(c)};
    \node at (+5.0,1.5) {(d)};
  \end{tikzpicture}
  \caption{\label{fig:parabolicTensions} The equilibrium tension
  distribution of a semipermeable vesicle with $\beta=10^{-3}$ in a parabolic
  flow (see Figure~\ref{fig:parabolicComposite}). The flow velocities
  are (a) 200$\mu$m/s, (b) 400$\mu$m/s, (c) 600$\mu$m/s, and (d)
  800$\mu$m/s.}
\end{figure*}

\subsection*{Vesicle in a Poiseuille flow}
In a nonlinear shear flow, an impermeable vesicle can reach equilibrium
position at the mid-plane of the shear flow for sufficiently large
reduced area, regardless of the maximum flow velocity $U$. For a
semi-permeable vesicle, however, our simulation results (summarized in
Figure~\ref{fig:parabolicComposite}) show that the equilibrium vesicle
shape and position are determined by $U$, and independent of the initial
vesicle reduced area and permeability $\beta$. The corresponding
membrane tension distribution is shown in
Figure~\ref{fig:parabolicTensions} as a function of flow velocity $U$
from $200\mu$m/s to $800\mu$m/s.

@@

\subsection*{Vesicle in a closely-fit channel}
When a semi-permeable vesicle goes through a closely-fit channel, we observe that the water efflux is found in the front, and the influx is in the rear of the vesicle membrane (Figure~\ref{fig:stenosisComposite}). This corresponds well to the corresponding tension distribution in Figure~\ref{fig:stenosisTensions}: Larger tension in the front, and smaller tension in the rear.
\begin{figure*}[htp]
  \centering
  \begin{tikzpicture}[scale=1]
    \node[inner sep=0pt] at (0,0) {
    \includegraphics[width=\textwidth]{figures/stenosisTensions.pdf}
    };
    \node at (-8.6,0.7) {(a)};
    \node at (-1.6,0.7) {(b)};
  \end{tikzpicture}
  \caption{\label{fig:stenosisTensions} The tension distribution along a
  semi-permeable vesicle going through a closely-fit channel of two
  different lengths.}
\end{figure*}

\subsection*{Vesicle going through a contracting channel (slit)}
When a semipermeable vesicle goes through a contracting channel (slit)
the numerical simulations show that both the driving flow and the
membrane permeability have to be sufficiently large for a successful
passage through the slit (see Figure~\ref{fig:contractingComposite}). As
the vesicle goes through the contracting channel, the gradual
confinement first leads to a slow inflation. Once the vesicle is close
to the neck, it quickly deflates in order to fit the constriction. When
the vesicle is near the neck, simulations show that the water efflux is
in the front and rear of vesicle while most water influx is in the
middle. The tension distribution along the vesicle as a function of
their position in the contracting channel is summarized in
Figure~\ref{fig:contractingTensions1}, where we observe the membrane
tension has the largest magnitude when the vesicle is at the neck. Away
from the neck the membrane tension is quite small due to th
\todo[inline]{I might have accidentally deleted some of your work here.
Sorry!}
\begin{figure*}[hbp]
  \centering
  \begin{tikzpicture}[scale=1]
    \node[inner sep=0pt] at (0,0) {
    \includegraphics[width=\textwidth]{figures/contractingTensions1.pdf}
    };
    \node at (-8.62,4.3) {(a)};
    \node at (+1.1,4.3) {(c)};
    \node at (-8.62,-1.2) {(b)};
    \node at (+1.1,-1.2) {(d)};
  \end{tikzpicture}
  \begin{tikzpicture}[scale=1]
    \node[inner sep=0pt] at (0,0) {
    \includegraphics[width=0.8\textwidth]{figures/contractingTensions2.pdf}
    };
    \node at (-6.79,1.4) {(e)};
  \end{tikzpicture}
  \caption{\label{fig:contractingTensions1} The tension distribution
  along a semi-permeable vesicle going through a contracting geometry.
  The vesicle tension increases by up to five orders of magnitude when
  as it enters the neck. The permeability constant and flow rates are
  (a) $U_{\max} = 5.7\mu$m/s, $\beta = 5 \times 10^{-4}$; (b) $U_{\max}
  = 5.7\mu$m/s, $\beta = 5 \times 10^{-3}$; (c) $U_{\max} = 0.57\mu$m/s,
  $\beta = 1 \times 10^{-3}$; (d) $U_{\max} = 5.7\mu$m/s, $\beta = 1
  \times 10^{-3}$; (e) $U_{\max} = 18\mu$m/s, $\beta = 1 \times
  10^{-3}$.}
\end{figure*}
